%-------------------------
% Resume in Latex
% Author : alex-dere
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}
\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    }


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}


\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}


%-------------------------
% Custom commands

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\small #2} % top row of resume entry
    \end{tabular*}
}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

    {\Large Derevyagin Alexander, Product Manager} \\ \vspace{5pt}
    \href{mailto:aleksandr.dereviagin@gmail.com}{aleksandr.dereviagin@gmail.com} \hspace{1pt} $|$ 
    github \hspace{1pt} $|$ 
    Tg: \href{https://t.me/aleks_amber}{@aleks\_amber}  \hspace{1pt} $|$ 
    \href{https://www.linkedin.com/in/alex-dere/}{www.linkedin.com/in/alex-dere/}
    \\ \vspace{20pt}


%-----------EXPERIENCE-----------


  \textbf{Summery}\\
  I  have been building B2B and B2C SaaS products as a consumer-facing \textbf{Product Manager for over 5 years}, and have 5 years experience in marketing. Most recently, \textbf{I developed and launched a no-code UI builder that helped to generate \$228,571 }for our client and a \textbf{Chatbot Platform generating \$85,714 in revenue}.\\
 I am a highly organized team-player focused on UX and data-driven approach.
\vspace{20pt}

\resumeSubheading
      {Yandex, Senior Product Manager}{2022 -- Present}  
\\
      
      \textcolor{gray}{\textit{Tech company valued at \$17.3B with 25K employees. Operates Russia's largest search engine, rivaling Google}}

Oversaw a SaaS CRM with 8 engineers, from \href{https://miro.com/app/board/uXjVK_QBCw0=/?moveToWidget=3458764591348909874&cot=14}{market research} and \href{https://miro.com/app/board/uXjVK_QBCw0=/?moveToWidget=3458764592116344712&cot=14}{user interviews} to deployment for 3K customers, aiming to boost Weekly Active Users (WAU), retention of CRM and revenue uplift for clients.
\begin{itemize}[itemsep=-5pt]
    \item Launched a no-code UI builder to create personal interfaces, resulting in a 9\% increase in WAU.
    \item Streamlined client transfer processes by rebuilding the data model and UI, generating \$228,571 yearly.
    \item Transitioned from Waterfall to Scrum, achieving a 30\% boost in task deadline predictability.
\end{itemize}
\vspace{20pt}

    \resumeSubheading
      {Mail, Product Manager}{2021 -- 2022}  
\\
      
      \textcolor{gray}{\textit{Tech company valued at \$6B with 7K employees. Operates Russia's largest social media platform, rivaling Meta}}

Developed and launched a no-code Chatbot Platform with a team of 30 engineers. Collaborated closely with the design team to optimize UX and UI, thereby increasing Onboarding Speed and chatbot Creation Efficiency.
\begin{itemize}[itemsep=-5pt]
    \item Developed a Chatbot Platform which resulted in the sale of 16 chatbots, generating \$85,714 in revenue.
    \item Increased revenue by \$28,571 through upselling marketing services to existing clients.
\end{itemize}
\vspace{20pt}
 
      \resumeSubheading
      {Social Discovery Group, Product Manager}{2017 -- 2020}  
\\
      
      \textcolor{gray}{\textit{One of the largest dating companies valued at \$28.7M, with 50M+ users and 800 employees}}

ecruited as Head of CRM Marketing in 2017, promoted to Product Manager of CRM in 2019. Led a marketing team with 2 managers and a team of 3 engineers to grow Revenue and LTV.
\begin{itemize}[itemsep=-5pt]
    \item Launched a Web-Push channel, resulting in a 5\% revenue growth.
    \item Integrated a recommendation system into emails, generating \$6,000 in the first week.
\end{itemize}
\vspace{20pt}


      \resumeSubheading
      {Previous work experience}{2014 -- 2017}  
\\ 
 
\begin{itemize}[itemsep=-5pt]
    \item Email marketer (project) at United-Traders.eu, 2017
    \item Email marketer at Spadream, 2016 -- 2017
    \item Marketing manager at Like BZ, 2015 -- 2016
    \item SMM manager at Vinigret, 2014 -- 2015
\end{itemize}
\vspace{20pt}

\textbf{Skills}
\begin{multicols}{2}
\begin{itemize}[itemsep=-5pt]
    \item SQL, HTML, Postman, BI 
    \item Figma, Miro, Adobe 
    \item Google Analytics/Trends 
    \item Jira, Trello, Slack 
    \item Salesforce, Asana 
\end{itemize}
\begin{itemize}[itemsep=-5pt]
    \item Market/Competitor research
    \item Data Analysis, Strategic planning, A/B
    \item UX, UI, CJM
    \item Leadership, negotiation
    \item Agile, SCRUM, Kanban
\end{itemize}
\end{multicols}


%-------------------------------------------
\end{document}
